A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-10 paper.tex
Modify Introduction

\begin{abstract} 
%cite IoT data subscription economy
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources. The real-time data exchangements among devices forms a publish/subscribe relationship of streaming data that increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any server or participants. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data trading platform on top of the IoT brokered infrastructure, in order to address the technical challenges. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts. Finally, the prototype is implemented and evaluated.
\end{abstract}

@@

\section{Introduction}
In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS} ,and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding the amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers ,and data consumers meet.

@@

In contrast to centralized architectures in \cite{DIaas, MARSA} that target to handle static data sets, we proposed a decentralized data trading infrastructure which aims for processing the high volume, high velocity and high variety of "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements. Moreover, a decentralized architecture can better adapt the dynamic roles than a centralized one. See Fig.~\ref{fig:system_design}.

We investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure, particularly Ethereum Smart Contract\cite{smartContract} and IOTA\cite{IOTAwhitepaper} Masked Authenticated Messaging (MAM)\cite{MAM}. The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency. Lastly, MAM as the data storage not only ensures the data integrity, but also enables access control and provides a scalable key and data management. These three keys meet the requirements mentioned previously.

>>>>

\begin{abstract} 
%cite IoT data subscription economy
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources. The real-time data exchangements among devices forms a publish/subscribe relationship of streaming data that increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data trading platform on top of the IoT brokered infrastructure, in order to address the technical challenges. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts. Finally, the prototype is implemented and evaluated.
\end{abstract}

@@

\section{Introduction}
In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories ,and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing platform where data providers and data consumers meet.

@@

In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we proposed a novel data trading infrastructure which aims for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData} while fulfills the aforementioned requirements. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV. Therefore, a publish/subscribe model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.

Proving the identity as well as the ownership of data is a challenging issue among various roles and large scale of platform. In current systems, trusted third-party authority like CA is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}.

Thus, the data trading platform for IoT towards a decentralized design. In this paper, 
we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure. See Fig.~\ref{fig:system_design}. The system collaborates Ethereum Smart Contract\cite{smartContract} and IOTA\cite{IOTAwhitepaper} Masked Authenticated Messaging (MAM)\cite{MAM}. The pub/sub model features the scalability and resource-efficiency, and the economic incentives are stimulated by regulating trading agreement and penalty on Ethereum Smart Contracts with transparency. Lastly, MAM as the data storage not only ensures the data integrity, but also enables access control and provides a scalable key and data management. A self-soverign identity system TangleID\cite{TangleID} is built on top of MAM as well. These three keys meet the requirements mentioned previously.
